### 2020-06-29 TCS_version/00-abstract.tex
minor updates

In the area of Natural Computing, reaction systems are
a qualitative abstraction inspired by the 
functioning of living cells, suitable to model the main
mechanisms of biochemical reactions.
This model has already been applied
and extended successfully to various areas of research. Reaction 
systems interact with the environment represented by the context, and
pose challenges for further extensions as well as
for the implementation, as it is a new computation model. 
In this paper {\color{red} we define a modular embedding of Reaction Systems as processes
in the chained Core Network Algebra (cCNA), which is a variant  of the  {\tt link}-calculus,
by representing the behaviour of each entity and
preserving faithfully their features, and we prove its correctness and completeness.}
%we consider a variant of the {\tt link}-calculus, which allows to model 
%multiparty interaction in concurrent systems, and show that we can
%represent reaction systems as processes 
%in a modular way, by representing the behaviour of each entity and
%preserving faithfully their features.
%We show the correctness and completeness 
%of our embedding.
%We illustrate our framework by 
{\color{red} We show} the embedding of 
a few examples expressing computer science
and biological applications. 
{\color{red}Our embedding provides a Labelled Transition System (LTS) semantics for reaction systems. Based on the LTS semantics, we adapt  the classical notion of  process bisimulation to define a bio-simulation relation for studying properties of reaction systems.}
%On top of the LTS semantics for reaction systems provided by our framework, 
%we then adapt the classical notion (in concurrency) of bisimulation
%to make it more suitable for studying properties of reaction systems.
In particular, we define a new assertion language based on regular expressions, 
which allows to specify the properties of interest, and use it to extend Hennessy-Milner logic
to our {\color{red} embedding.}
% framework. 
{\color{red} We prove that our bio-simulation relation and the logical equivalence, that are defined parametrically on some assertion of interest, coincide.}
%Interestingly, the novel notion of bisimilarity and logical equivalence that are defined parametrically on some assertion of interest are proved to coincide, like in the classical case.
Finally, 
{\color{red} we claim that}
our methodology 
%can 
contribute to increase the expressiveness
of reaction systems, by exploiting the interaction among 
different reaction systems.

>>>>

In the area of Natural Computing, Reaction Systems (RSs) are
a qualitative abstraction inspired by the 
functioning of living cells, suitable to model the main
mechanisms of biochemical reactions.
%This model has already been applied
%and extended successfully to various areas of research. 
RSs interact with a context, and
pose challenges for modularity, compositionality, extendibility and behavioural equivalence. 
In this paper we define a modular encoding of RSs as processes
in the chained Core Network Algebra (cCNA), which is a new variant  of the  {\tt link}-calculus.
The encoding represents the behaviour of each entity separately and
preserves faithfully their features, and we prove its correctness and completeness.
%we consider a variant of the {\tt link}-calculus, which allows to model 
%multiparty interaction in concurrent systems, and show that we can
%represent reaction systems as processes 
%in a modular way, by representing the behaviour of each entity and
%preserving faithfully their features.
%We show the correctness and completeness 
%of our embedding.
%We illustrate our framework by 
%{\color{red} We show} the embedding of 
%a few examples expressing computer science
%and biological applications. 
Our encoding provides a Labelled Transition System (LTS) semantics for RSs. Based on the LTS semantics, we adapt  the classical notion of  bisimulation to define a novel equivalence, called bio-similarity, for studying properties of RSs.
%On top of the LTS semantics for reaction systems provided by our framework, 
%we then adapt the classical notion (in concurrency) of bisimulation
%to make it more suitable for studying properties of reaction systems.
In particular, we define a new assertion language based on regular expressions, 
which allows to specify the properties of interest, and use it to extend Hennessy-Milner logic
to our setting.
% framework. 
We prove that our bio-similarity relation and the logical equivalence, that are defined parametrically on some assertion of interest, coincide.
%Interestingly, the novel notion of bisimilarity and logical equivalence that are defined parametrically on some assertion of interest are proved to coincide, like in the classical case.
Finally, 
we claim that
our encoding 
%can 
contributes to increase the expressiveness
of RSs, by exploiting the interaction among 
different RSs.

### 2020-06-29 TCS_version/01-introduction.tex
minor updates

Natural Computing is an emerging area of research which has two main 
aspects: human designed computing inspired by nature, and computation 
performed in nature. Reaction Systems (RSs)~\cite{BEMR11} are 
% model of
% formal computation 
a rewriting formalism
%model 
inspired by the way biochemical reactions take place in living 
cells.  
This theory has already shown to be relevant in several different 
fields, such as computer science~\cite{MPR15}, 
biology~\cite{ABP14,CMMBM12,Az17,BarbutiGLM16}, 
molecular chemistry~\cite{OY16}.
%,
% and it
%is continuously developing, with a growing number of workshops and
%international meetings. 
Reaction Systems formalise the mechanisms of biochemical systems, 
such as {\em facilitation} and {\em inhibition}. 
As a qualitative approximation of the real biochemical reactions, they
% do not take
%into account the quantity of reagents effectively present. They
consider if a necessary reagent is or not present, and likewise they
consider if an inhibiting molecule is or not present. 
The  possible reactants and inhibitors are called `entities'.
RSs model in a direct way the interaction of a living cell
with the environment (called `context'). However, two RSs are seen
as independent models and do not interact.

%Formally, Reaction Systems are defined as a rewriting formalism.
%In this paper, we present an encoding from RSs, 
%to the  open multiparty process algebra c\CNA,\footnote{After `chained Core Network 
%Algebra'.} a variant of the {\tt link}-calculus~\cite{BodeiBB12,BBB17} without name mobility.
{\color{red}In this paper, we present an embedding
%encoding 
from RSs, 
to the chained Core Network  Algebra (c\CNA), first defined in~\cite{BBF19}, a variant of the 
 open multiparty process algebra~\CNA~\cite{BBB17}; the \CNA~equipped with mobility is referred to as the {\tt link}-calculus~\cite{BODEI2020104587}}.
This formalism allows several processes to synchronise and 
communicate altogether, at the same time, with a new interaction
mechanism based on links and link chains. 
The initial motivation for introducing
{\color{red} an open multiparty mechanism}
% this mechanism 
was to encode
Mobile Ambients~\cite{CardelliG00}, getting a much stronger operational
correspondence than any available in the literature, such as the one in~\cite{B16}.
Later it was shown that the {\tt link}-calculus allowed one to easily encode calculi for biology equipped with membranes, as in~\cite{BodeiBBC14}.

@@

Our main contributions are as follows:
\begin{itemize}
\item the behaviour of the context, for each single 
entity,
%\footnote{Entities that belong to the `domain' of a RS.}
can be
specified in a recursive way, as ordinary processes;
\item along the same lines, non-deterministic contexts can be seamlessly expressed in our setting; 
\item when deterministic contexts are considered, the c\CNA \
computation is deterministic and mimics the evolution of the corresponding RS;
\item we define an assertion language to specify local properties of 
Reaction Systems and exploit it to define a novel notion of behavioural equivalence for 
RSs,
%Reaction Systems, 
called bio-similarity;
\item we show that our assertions can be used to extend the Hennessy-Milner logic to our 
%framework
{\color{red}embedding}, in such a way that logical equivalence of processes coincide with bio-similarity;
\item we sketch how one can express the behaviour of entity mutation,
%change the behaviour of  each single entity $s$  in a
%way that a mutation $s'$ can be expressed; 
in such a way that {\color{red} the mutated version of the entity
$s$ can}  take part to only a subset of rules requiring entity $s$;
\item we show that with a little coding effort, our 
%encoding 
{\color{red} embedding}
allows two RSs to
communicate; i.e. we can model scenarios where a subset of those entities that the context  can
provide, are instead provided by a second RS.
\end{itemize}

The main drawback of our proposal, is that the {\color{red} resulting c\CNA \ 
code}
%translation 
is
verbose. Nevertheless it is clear that our
%translation 
{\color{red} embedding}
can be automatised by means of a proper front-end in
an implementation of the {\tt link}-calculus. 
The examples that we propose also show that some optimisations are possible
to reduce the coding when suitable assumptions are made about the provision of entities.

As we have remarked, in our 
%translation,
{\color{red} embedding}
 Reaction Systems 
get the ability to interact between them in a synchronized manner. 
This interaction is not foreseen in
the basic RS framework, as it can only happen with the context.
{\color{red}The proposed network of reaction systems~\cite{BLR20} allows
any reaction system in the network to receive entities 
produced from its neighbors (that will represent its context), with the hypothesis that  
reaction systems without neighbors will receive no entities 
from the context. 
In our case, a RS can receive some entities from the context and some others from a second RS, in any case we always assume contextes having a non-determinist behaviour.
}
By exploiting recursion, the kind of interactions which can be 
defined can be complex and expressive.
Example~\ref{ex:twoRS} and more in general the discussion in 
Section~\ref{subsec:comRS}
%~\ref{sec:discussion}
 show that 
the interaction between RSs can help to model new scenarios.

@@

Process calculi have been used successfully to model
biological processes, see~\cite{BBDFH18} for a recent survey.
We are not aware of any 
%SOS 
structural operational semantics for the RS; it seems not the case
that a deterministic behaviour, as the one of the RS, once the initial state is 
fixed, could be defined by inference rules that classically are applied 
to define non-deterministic transition systems.
The reversible computation paradigm for RS extends the RS framework  by
allowing  backward computations as well as forward computations; for this 
goal a set of inference rules for rewriting logic has been 
defined in~\cite{10.1007/978-3-319-73359-3_3}
to exactly keep trace of those elements that  dissolve in the next 
computation step.

A preliminary version of this paper appeared in~\cite{BBF19}.
There are several major differences w.r.t. the paper~\cite{BBF19}, which is here extended as follows:
\begin{itemize}
\item we present several new examples to illustrate our 
{\color{red} embedding},
%framework,
and give more detailed explanations about its use;
\item we introduce an assertion language to specify the properties of RSs;
%Reaction Systems;
\item we define the notion of bio-simulation to relate RSs
%Reaction Systems 
and compare their behaviours;
\item we show that our assertion language allows to specify properties extending to our
{\color{red} embedding}
%framework 
the Hennessy-Milner logic;
\item we include here all proofs of main results.
\end{itemize}

>>>>

Natural Computing is an active area of research which builds on two main 
aspects: human designed computing inspired by nature, and computation 
performed in nature. Reaction Systems (RSs)~\cite{BEMR11} are 
% model of
% formal computation 
a rewriting formalism
%model 
inspired by the way biochemical reactions take place in living 
cells.  
This theory has already shown to be relevant in several different 
fields, 
%such as computer science~\cite{MPR15}, 
including biology~\cite{ABP14,CMMBM12,Az17,BarbutiGLM16}
and molecular chemistry~\cite{OY16}.
%,
% and it
%is continuously developing, with a growing number of workshops and
%international meetings. 
RSs formalise the mechanisms of biochemical systems, 
such as {\em facilitation} and {\em inhibition}. 
As a qualitative approximation of the real biochemical reactions, they
% do not take
%into account the quantity of reagents effectively present. They
consider if a necessary reagent is or not present, and likewise they
consider if an inhibiting molecule is or not present. 
The  possible reactants and inhibitors are called `entities'.
RSs model in a direct way the interaction of a living cell
with the environment (called `context'). However, two RSs are seen
as independent models and do not interact.

%Formally, Reaction Systems are defined as a rewriting formalism.
%In this paper, we present an encoding from RSs, 
%to the  open multiparty process algebra c\CNA,\footnote{After `chained Core Network 
%Algebra'.} a variant of the {\tt link}-calculus~\cite{BodeiBB12,BBB17} without name mobility.
In this paper, which is an extended version of~\cite{BBF19},
we present an encoding
%encoding 
from RSs
to the chained Core Network  Algebra (c\CNA), a variant of the 
 open multiparty process algebra~\CNA~\cite{BBB17}; the \CNA~equipped with mobility is referred to as the {\tt link}-calculus~\cite{BodeiBB12,BODEI2020104587}.
 Here mobility is not needed.
This formalism allows several processes to synchronise and 
communicate altogether, at the same time, with a new interaction
mechanism based on links and link chains. 
The initial motivation for introducing
an open multiparty mechanism in~\cite{BodeiBB12}
% this mechanism 
was to encode
Mobile Ambients~\cite{CardelliG00}, getting a much stronger operational
correspondence than any available in the literature, such as the one in~\cite{B16}.
Later it was shown that the {\tt link}-calculus allowed one to easily encode calculi for biology equipped with membranes, as in~\cite{BodeiBBC14}.

@@

Our main contributions are as follows:
\begin{itemize}
\item any context is represented as an ordinary c\CNA \ process, which allows us to specify recursive and non-deterministic contexts in a natural way; 
when deterministic contexts are considered, as in ordinary RSs, the c\CNA \
computation is also deterministic and matches the evolution of the underlying RS;
\item we define an assertion language to specify local properties of 
RSs and exploit it to define a novel notion of behavioural equivalence,
%Reaction Systems, 
called bio-similarity;
\item we show that our assertions can be used to extend the Hennessy-Milner's logic to our 
%framework
encoding, in such a way that logical equivalence of processes coincide with bio-similarity.
\end{itemize}

Moreover, we sketch how the encoding can be used to enhance the expressivity of RSs along different dimensions:
\begin{itemize}
\item we sketch how one can express the behaviour of entity mutation,
%change the behaviour of  each single entity $s$  in a
%way that a mutation $s'$ can be expressed; 
in such a way that the mutated version of the entity
$s$ can  take part to only a subset of rules requiring entity $s$;
\item we sketch how with a little coding effort, our 
%encoding 
embedding
allows two RSs to
communicate; i.e. we can model scenarios where a subset of those entities that the context  can
provide, are instead provided by a second RS.
\end{itemize}

The main drawback of our proposal, is that the resulting c\CNA \ 
code
%translation 
is
verbose. Nevertheless it is clear that our
%translation 
encoding
can be automatised by means of a proper front-end in
an implementation of the {\tt link}-calculus. 
The examples that we propose also show that some optimisations are possible
to reduce the coding when suitable assumptions are made about the provision of entities.

As we have remarked, in our 
%translation,
encoding
the entities and the reactions
get the ability to interact in a synchronous manner. 
This interaction is not foreseen in
the basic RS framework, as it can only happen once the context is provided.
The proposed network of RSs~\cite{BLR20} allows
any RS in the network to receive entities 
produced from its neighbours (that will represent its context), with the hypothesis that  
RSs without neighbours will receive no entities 
from the context. 
In our case, a RS can receive some entities from the context and some others from a second RS; moreover we can represent contexts having a recursive, non-determinist behaviour.
%
By exploiting recursion, the kind of interactions which can be 
defined can be complex and expressive.
Example~\ref{ex:twoRS} and more in general the discussion in 
Section~\ref{subsec:comRS}
%~\ref{sec:discussion}
 show that 
the interaction between RSs can help to model new scenarios.

@@

Process calculi have been used successfully to model
biological processes, see~\cite{BBDFH18} for a recent survey.
We are not aware of any 
%SOS 
structural operational semantics for RS; it seems not the case
that a deterministic behaviour, as the one of the RS, once the initial state is 
fixed, could be defined by inference rules that classically are applied 
to define non-deterministic transition systems.
The reversible computation paradigm for RS extends the RS framework  by
allowing  backward computations as well as forward computations; for this 
goal a set of inference rules for rewriting logic has been 
defined in~\cite{10.1007/978-3-319-73359-3_3}
to exactly keep trace of those elements that  dissolve in the next 
computation step.

As already mentioned, a preliminary version of this paper appeared in~\cite{BBF19}.
There are several major differences w.r.t. the conference version~\cite{BBF19}, which is here extended as follows:
\begin{itemize}
\item we present several new examples to illustrate our 
 encoding,
%framework,
and give more detailed explanations about its use;
\item we introduce an assertion language to specify the properties of RSs;
%Reaction Systems;
\item we define the notion of bio-simulation to relate RSs
%Reaction Systems 
and compare their behaviours;
\item we show that our assertion language allows to specify properties extending to our
encoding
%framework 
the Hennessy-Milner logic;
\item we include here all proofs of main results.
\end{itemize}

### 2020-06-29 TCS_version/02-ReactionSystem.tex
altri piccoli cambiamenti
minor updates

% !TEX root = ./main_RS2L_LNCS.tex

\section{Reaction Systems}
\label{sec:rs}

@@

The mechanisms that are at the basis of biochemical reactions and thus 
regulate the functioning of a living cell, are 
{\em facilitation} and {\em inhibition}. These mechanisms are 
reflected in the basic definitions of Reaction Systems.

\begin{definition}[Reaction]
A reaction is a triplet $a = (R,I,P)$, where $R, I, P$ are finite,  
non empty sets  and
$R \cap I = \emptyset$. If $S$ is a set such that  $R, I, P \subseteq S$, 
then $a$ is a reaction in $S$.
\end{definition}

@@

\begin{definition}[Reaction System]
A Reaction System (RS) is an ordered pair ${\cal A} = (S, A)$ 
such that $S$ is a finite set, and $A \subseteq rac(S)$.
%The set $S$ is called the background (set) of $A$.\\
%The main notion concerning the functioning of a reaction system is defined 
%as follows.
\end{definition}

The set $S$ is called the \emph{background set} of ${\cal A}$, its elements are called \emph{entities},
they represent molecular substances (e.g., atoms, ions, molecules) that may be present
in the states of a biochemical system.
% modeled by $A$. 
The set $A$ is the set of \emph{reactions} of $\mathcal{A}$.
Since $S$ is finite, so is $A$: 
we denote by $|A|$ the number of reactions in $A$.

\begin{definition}[Reaction Result]
Let $W$ be a finite subset of $S$.
\begin{enumerate}
\item Let $a$ be a reaction in $S$. Then $a$ is enabled by $W$, denoted by $\mathit{en}_a(W)$, 
if $R_a \subseteq W$
and $I_a \cap W = \emptyset$. The result of $a$ on $W$, denoted by $\mathit{res}_a(W)$, 
is defined by:
$\mathit{res}_a(W) =P_a$, if $\mathit{en}_a(W)$, and $\mathit{res}_a(W) = \emptyset$ otherwise.
\item Let $A$ be a finite set of reactions. The result of $A$ on $W$, denoted 
by $\mathit{res}_A(W)$,  is defined
by: $\mathit{res}_A(W) = \bigcup_{a \in A} \mathit{res}_a(W)$.
\end{enumerate}
\end{definition}

@@

\begin{definition}[Interactive Process]
Let ${\cal A} = (S, A)$ be a RS and let $n \geq 0$. 
An $n$-step
\emph{interactive process} in ${\cal A}$ is a pair $\pi = (\gamma, \delta)$ of 
finite sequences s.t.
%
%\begin{center}
$ \gamma=\{C_i\}_{i\in[0,n]}$  and $\delta=\{D_i\}_{i\in[0,n]} $
%$\gamma = C_0, \dots , C_n$ and $\delta = D_0, \dots , D_n$, 
%\end{center}
%\noindent
where 
$ C_{i}, D_{i}  \subseteq S$ for any $i\in[0,n]$, $D_0 = \emptyset$, and 
%$C_0,\dots, C_n, D_0,\dots, D_n  \subseteq S$, $D_0 = \emptyset$, and 
$D_i =  \mathit{res}_{A}(D_{i-1} \cup C_{i-1})$ for any $i \in [1,n]$.
% $i \in \{1,\dots, n\}$.
\end{definition}

Living cells are seen as open systems that continuously react with 
the external environment, in discrete steps. 
The sequence $\gamma$ is the {\em context sequence} of $\pi$ and 
represents the influence of the environment on the Reaction System.
The sequence $\delta$ is
the {\em result sequence} of $\pi$ and it is entirely determined by $\gamma$ and $A$.
%
The sequence $\tau = W_{0}, \ldots, W_{n}$ with $W_{i} = C_{i} \cup D_{i}$, 
for any $i \in [0, n]$
%, and $D_{0} = \emptyset$ 
is called a \emph{state sequence}.
%
Each state $W_{i}$ in a state sequence
is the union of two sets: the context $C_{i}$
at step $i$ and the result $D_i=\mathit{res}_{A}(W_{i-1})$ from the previous step.

@@

For technical reasons, we extend the notion of an interactive process to deal with 
infinite sequences.

>>>>

% !TEX root = ./main_TCS.tex

\section{An Overview of Reaction Systems}
\label{sec:rs}

@@

The mechanisms that are at the basis of biochemical reactions and thus 
regulate the functioning of a living cell, are 
{\em facilitation} and {\em inhibition}. These mechanisms are 
reflected in the basic definitions of RSs.

\begin{definition}[Reaction]
Let $S$ be a set of entities.
A reaction over $S$ is a triplet $a = (R,I,P)$, where $R, I, P$ are finite,  
non empty subsets of $S$ and
$R \cap I = \emptyset$. 
%If $S$ is a set such that  $R, I, P \subseteq S$, 
%then $a$ is a reaction in $S$.
\end{definition}

@@

\begin{definition}[Reaction System]
A Reaction System (RS) is an ordered pair ${\cal A} = (S, A)$ 
such that $S$ is a finite set of  entities, and $A \subseteq rac(S)$ is a set of reactions over $S$.
%The set $S$ is called the background (set) of $A$.\\
%The main notion concerning the functioning of a reaction system is defined 
%as follows.
\end{definition}

The set $S$ is called the \emph{background set} of ${\cal A}$; its elements represent molecular substances (e.g., atoms, ions, molecules) that may be present
in the states of a biochemical system.
% modeled by $A$. 
The set $A$ is the set of \emph{reactions} of $\mathcal{A}$.
Since $S$ is finite, so is $A$: 
we denote by $|A|$ the number of reactions in $A$.

\begin{definition}[Reaction Result]
Given a set of entities $S$, let $W\subseteq S$ be a finite subset of  entities.
\begin{enumerate}
\item Let $a$ be a reaction over $S$. Then $a$ is enabled by the entities in the set $W$, denoted by $\mathit{en}_a(W)$, 
if $R_a \subseteq W$ and $I_a \cap W = \emptyset$, i.e. all the reactants of $a$ are in $W$,
 while none of the inhibitors of $a$ are in $W$. The result of $a$ on $W$, denoted by $\mathit{res}_a(W)$, 
is defined by:
$\mathit{res}_a(W) \defeq P_a$, if $\mathit{en}_a(W)$, and $\mathit{res}_a(W) \defeq \emptyset$ otherwise.
\item Let $A$ be a finite set of reactions over $S$. The result of $A$ on $W$, denoted 
by $\mathit{res}_A(W)$,  is defined
by: $\mathit{res}_A(W) \defeq \bigcup_{a \in A} \mathit{res}_a(W)$.
\end{enumerate}
\end{definition}

@@

\begin{definition}[Interactive Process]
Let ${\cal A} = (S, A)$ be a RS and let $n$
% \geq 0$.
be a nonnegative integer;   
An $n$-step
\emph{interactive process} in ${\cal A}$ is a pair $\pi = (\gamma, \delta)$ of 
finite sequences s.t.
%
%\begin{center}
$ \gamma=\{C_i\}_{i\in[0,n]}$  and $\delta=\{D_i\}_{i\in[0,n]} $
%$\gamma = C_0, \dots , C_n$ and $\delta = D_0, \dots , D_n$, 
%\end{center}
%\noindent
where 
$ C_{i}, D_{i}  \subseteq S$ are set of entities for any $i\in[0,n]$, $D_0 = \emptyset$, and 
%$C_0,\dots, C_n, D_0,\dots, D_n  \subseteq S$, $D_0 = \emptyset$, and 
$D_i =  \mathit{res}_{A}(D_{i-1} \cup C_{i-1})$ for any $i \in [1,n]$.
% $i \in \{1,\dots, n\}$.
\end{definition}

Living cells are seen as open systems that continuously react with 
the external environment, in discrete steps. 
The sequence $\gamma$ is the {\em context sequence} of $\pi$;
it can be arbitrarily defined and 
represents the influence of the environment on the 
RS.
%Reaction System.
The sequence $\delta$ is
the {\em result sequence} of $\pi$ and it is entirely determined by $\gamma$ and $A$.
%
The sequence $\tau = W_{0}, \ldots, W_{n}$ with $W_{i} = C_{i} \cup D_{i}$, 
for any $i \in [0, n]$
%, and $D_{0} = \emptyset$ 
is called a \emph{state sequence}.
%
Each state $W_{i}$ in a state sequence
is the union of two sets: the context $C_{i}$
at step $i$ and the result $D_i=\mathit{res}_{A}(W_{i-1})$ from the previous step.

@@

Since we will be able to deal with recursively contexts, we extend the notion of an interactive process to deal with 
infinite sequences.

### 2020-06-29 TCS_version/04-CCNA.tex
minor updates

In this section we introduce  the syntax and operational semantics
of a variant of the {\tt link}-calculus~\cite{BodeiBB12}, the c\CNA\  (chained \CNA)
where the prefixes are link chains and not just links.
%In this section we just focus on the basic ideas of link
% interaction, while we shall enhance the model with name mobility in
% the next section.

>>>>

In this section we introduce  the syntax and operational semantics
of the process algebra c\CNA\  (chained \CNA) to be used for encoding RSs.
As already explained in the Introduction, c\CNA\ is a variant of \CNA~\cite{BBB17}, the non-mobile
fragment of {\tt link}-calculus~\cite{BodeiBB12,BODEI2020104587}.
In c\CNA\  the action prefixes are link chains and not just links.
%In this section we just focus on the basic ideas of link
% interaction, while we shall enhance the model with name mobility in
% the next section.
